A Survey of Range-Only SLAM Techniques and Sensors

### 2018-01-29 Paper.tex
Graph slam

	\subsection{Graph SLAM}

>>>>

\begin{figure}[h!]
	\centering
	\includegraphics[height=70mm,width=90mm]{graph_slam.PNG}
	\caption{$z_k,\mu_k,x_k$ represents the measurement contraints, velocity constraints and the the robot path.}

\subsection{Graph SLAM}
Graph SLAM unlike the EKF solves the full SLAM problem. It is similar to the information filter in the way it represents the Gaussian  in the form of its information filter and information matrix. The key difference is in the sparseness maintained in the information matrix due to linearizion in graph SLAM as mentioned in[Probablisitic robotics]. This allows for the use of variable elimination algorithms and also maintain higher dimensional maps which were not possible using EKF.

It represents the information in the form of a graph as show in figure. The nodes in the graph represent the robots path and the landmarks. The edges between them represents the spatial  constraints between them also known as information constraints. These constraints ae then linearised and are applied through standard inference techniques to acquire the full posterior.A manifold graph SLAM algorithm has been mentioned in [ turorial in graph slam].
